Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-30 paper/reply.tex
improved Preliminaries (R1)

\noindent Since our stability analysis is based on polynomial coefficients
and not over signals, in Equation (8) $\Delta_{q} G$ is a model that incorporates 
the effects of $\nu$ in $\vec{\hat{G}}$, in order to investigate the system's 
stability consequences.

>>>>

\noindent Since our stability analysis is based on polynomial coefficients
and not over signals, Equation (8) incorporates the effects of $\nu$ in $\vec{\hat{G}}$
(by means of $\Delta_{q} G$), in order to investigate the system's stability consequences.
